### 2018-04-26 doc/paper.tex
Added pseudocode for basic de Casteljau.
Also changing approach to algorithm in LaTeX.
Adding compensated de Casteljau as an algorithm.
Also adding the forgotten `res` and `n` variables.
Adding an abstract.

\usepackage{amsthm,amssymb,amsmath}
%% H/T: https://tex.stackexchange.com/a/202168/32270
\usepackage{textcomp}
%% H/T: https://tex.stackexchange.com/a/215651/32270
\usepackage[ruled]{algorithm2e}

@@

@@

\begin{algorithm}[H]
  \textit{function} \(\left[x, y\right] = \mathtt{TwoSum}(a, b)\) \\
  \quad \(x = a \oplus b\) \\
  \quad \(z = x \ominus a\) \\
  \quad \(y = (a \ominus (x \ominus z)) \oplus (b \ominus z)\)

  \caption{\textit{EFT of the sum of two floating point numbers.}}
\end{algorithm}

\begin{algorithm}[H]
  \textit{function} \(\left[x, y\right] = \mathtt{Split}(a)\) \\
  \quad \(z = a \otimes (2^r + 1)\) \\
  \quad \(x = z \ominus (z \ominus a)\) \\
  \quad \(y = a \ominus x\)

  \caption{\textit{Splitting of a floating point number into two parts.}}
\end{algorithm}

\begin{algorithm}[H]
  \textit{function} \(\left[x, y\right] = \mathtt{TwoProd}(a, b)\) \\
  \quad \(x = a \otimes b\) \\
  \quad \(\left[a_h, a_l\right] = \mathtt{Split}(a)\) \\
  \quad \(\left[b_h, b_l\right] = \mathtt{Split}(b)\) \\
  \quad \(y = a_l \otimes b_l \ominus (((x \ominus a_h \otimes b_h)
      \ominus a_l \otimes b_h) \ominus a_h \otimes b_l)\)

  \caption{\textit{EFT of the product of two floating point numbers.}}
\end{algorithm}

\begin{algorithm}[H]
  \textit{function} \(\left[x, y\right] = \mathtt{TwoProdFMA}(a, b)\) \\
  \quad \(x = a \otimes b\) \\
  \quad \(y = \mathtt{FMA}(a, b, -x)\)

  \caption{\textit{EFT of the sum of two floating point numbers with a FMA.}}
\end{algorithm}

>>>>

\usepackage{amsthm,amssymb,amsmath}
%% H/T: https://tex.stackexchange.com/a/202168/32270
\usepackage{textcomp}
%% H/T: https://tex.stackexchange.com/a/56877/32270
\usepackage{algorithm}
\usepackage{algpseudocode}

@@

\begin{abstract}
In computer aided geometric design a polynomial is usually represented in
Bernstein form. This paper presents a family of compensated algorithms to
accurately evaluate a polynomial in Bernstein form with floating point
coefficients. The principle is to apply error-free transformations to
improve the traditional de Casteljau algorithm. At each stage of computation,
round-off error is passed on to first order errors, then to second order
errors, and so on. After the computation has been ``filtered'' \(K\)-times
via this process, the resulting output is as accurate as the de Casteljau
algorithm performed in \(K\) times the working precision. Forward error
analysis and numerical experiments illustrate the accuracy of this family
of algorithms.
\end{abstract}

@@

\begin{algorithm}[H]
  \caption{\textit{EFT of the sum of two floating point numbers.}}

  \begin{algorithmic}
    \Function{\(\left[x, y\right] = \mathtt{TwoSum}\)}{$a, b$}
      \State \(x = a \oplus b\)
      \State \(z = x \ominus a\)
      \State \(y = (a \ominus (x \ominus z)) \oplus (b \ominus z)\)
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
  \caption{\textit{Splitting of a floating point number into two parts.}}

  \begin{algorithmic}
    \Function{\(\left[x, y\right] = \mathtt{Split}\)}{$a$}
      \State \(z = a \otimes (2^r + 1)\)
      \State \(x = z \ominus (z \ominus a)\)
      \State \(y = a \ominus x\)
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
  \caption{\textit{EFT of the product of two floating point numbers.}}

  \begin{algorithmic}
    \Function{\(\left[x, y\right] = \mathtt{TwoProd}\)}{$a, b$}
      \State \(x = a \otimes b\)
      \State \(\left[a_h, a_l\right] = \mathtt{Split}(a)\)
      \State \(\left[b_h, b_l\right] = \mathtt{Split}(b)\)
      \State \(y = a_l \otimes b_l \ominus (((x \ominus a_h \otimes b_h)
          \ominus a_l \otimes b_h) \ominus a_h \otimes b_l)\)
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
  \caption{\textit{EFT of the sum of two floating point numbers with a FMA.}}

  \begin{algorithmic}
    \Function{\(\left[x, y\right] = \mathtt{TwoProdFMA}\)}{$a, b$}
      \State \(x = a \otimes b\)
      \State \(y = \mathtt{FMA}(a, b, -x)\)
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
  \caption{\textit{de Casteljau algorithm for polynomial evaluation.}}

  \begin{algorithmic}
    \Function{\(\mathtt{res} = \mathtt{DeCasteljau}\)}{$p, s$}
      \State \(n = \texttt{length}(p) - 1\)
      \State \(r = 1 \ominus s\)
      \\
      \For{\(j = 0, \ldots, n\)}
        \State \(b_j^{(n)} = p_j\)
      \EndFor
      \\
      \For{\(k = n - 1, \ldots, 0\)}
        \For{\(j = 0, \ldots, k\)}
          \State \(b_j^{(k)} = \left(r \otimes b_j^{(k + 1)}\right) \oplus
              \left(s \otimes b_{j + 1}^{(k + 1)}\right)\)
        \EndFor
      \EndFor
      \\
      \State \(\mathtt{res} = b_0^{(0)}\)
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
  \caption{\textit{Compensated de Casteljau algorithm for polynomial evaluation.}}

  \begin{algorithmic}
    \Function{\(\mathtt{res} = \mathtt{CompDeCasteljau}\)}{$p, s$}
      \State \(n = \texttt{length}(p) - 1\)
      \State \(\left[r, \rho\right] = \mathtt{TwoSum}(1, -s)\)
      \\
      \For{\(j = 0, \ldots, n\)}
        \State \(b_j^{(n)} = p_j\)
        \State \(e_j^{(n)} = 0\)
      \EndFor
      \\
      \For{\(k = n - 1, \ldots, 0\)}
        \For{\(j = 0, \ldots, k\)}
          \State \(\left[P_1, \pi_1\right] = \mathtt{TwoProd}\left(
              r, b_j^{(k + 1)}\right)\)
          \State \(\left[P_2, \pi_2\right] = \mathtt{TwoProd}\left(
              s, b_{j + 1}^{(k + 1)}\right)\)
          \State \(\left[b_j^{(k)}, \sigma_3\right] = \mathtt{TwoSum}(
              P_1, P_2)\)
          \State \(w = \pi_1 \oplus \pi_2 \oplus \sigma_3 \oplus
              \left(\rho \otimes b_j^{(k + 1)}\right)\)
          \State \(e_j^{(k)} = w \oplus \left(s \otimes e_{j + 1}^{(k + 1)}
              \right) \oplus \left(r \otimes e_j^{(k + 1)}\right)\)
        \EndFor
      \EndFor
      \\
      \State \(\mathtt{res} = b_0^{(0)} \oplus e_0^{(0)}\)
    \EndFunction
  \end{algorithmic}
\end{algorithm}
